Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-01-30 revisionMemo/rev1.tex
reviewer 1 issue

		TO DO/CD: We have revised this opening statement to clarify our position. Max: I'm wondering if we should combine this with the Q above or is R1's question here distinct enough?

>>>>

		TO DO/CD: We have revised this opening statement to clarify that the problem is treating dyads as independent, not stacking them.
